\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{cite}
\usepackage{forest}

\newcommand{\up}[2]{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny #2}}}{#1}}}
\newcommand{\T}[0]{{\mathcal{T}_r^h}}
\newcommand{\he}[0]{\textit{height}}
\newcommand{\ro}[0]{\textit{root}}
\newcommand{\SUB}[0]{\textit{sub}}
\newenvironment{statement2}[2]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2}]}{\end{trivlist}}
\newenvironment{statement3}[3]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2} {#3}\textbf{.}]}{\end{trivlist}}

\setlength{\parindent}{0pt}
\begin{document}
\title{Kraft's and McMillan's Inequalities}
\author{Phil Pützstück, 377247\\
Proseminar Informationstheorie, Steffen van Bergerem}
\maketitle

\begin{abstract}
    We study the existence of uniquely decodable or instantaneous $r$-ary codes for some given word-lengths.
    To do this, we prove and discuss the known Kraft and McMillan Inequalities by utilising graph theory.
    The approach is based on \cite{ICT}.
\end{abstract}

\section*{Introduction}
As uniquely decodable $r$-ary codes and instantaneous codes are important concepts,
we want to know under which constraints these exist.
We specifically look at $r$-ary codes with given word-lengths, as the inequalities
we will later prove relate these concepts. After introducing a certain rooted Tree we show the relation between them and $r$-ary codes, which we use in the proof for Kraft's Inequality. Following the proofs we discuss the implications of these inequalities and give an example.
For a quick introduction to our graph-terminology:\\[10pt]
Consider a tree, which is defined to be an acyclic, connected and undirected graph.
A tree $T = (V,E)$ has the set of vertices $V$ and the set of edges $E$, which we denote by $V(T) := V, E(T) := E$.
We call $T$ a rooted tree, if we have a distinct vertex $v \in V(T)$,
called the root of $T$ and denoted as $\ro(T) = v$.
Note that we then have a unique path from the root of $T$ to each vertex of $T$.
In this case each vertex $v \in V(T)$ has a height, denoted $\he(v) = \he_T(v)$,
defined as the length of that unique path from $\ro(T)$ to $v$.\\[10pt]
For the rest of this paper we will only consider rooted trees, in particular $r$-ary rooted trees of some height $h$, where $r,h \in \mathbb{N}$, which
are rooted trees of finite height $h$ where each vertex of height less than $h$ has exactly $r$ children.
We introduce subtrees and an ordering of vertices:

\begin{statement3}{(1.1)}{Definition}{(Subtrees and Ordering)}\strut\\[2pt]
    Let $T, T'$ be rooted Trees. We say $T'$ is a rooted subtree of $T$, iff $T'$ is a subgraph of $T$ and write
    $T' \leq T$. We write $T' \leq_r T$ iff $r \in \mathbb{N}$ and $T,T'$ are both $r$-ary.
    Now let $v,w \in V(T)$. We write $v \leq w$ iff the unique path from $\ro(T)$ to $w$ visits $v$.
    Let $v \in T \setminus \{\ro(T)\}$. Set
    $V_v := \{u \in V(T) \mid v \leq u\}, E_v := \{(u,u') \in E(T) \mid u,u' \in V_v\}$
    and let $\SUB(v) = \SUB_T(v) := (V_v, E_v)$ be the rooted subtree of $T$ with $v$ as its root.
    At last we define $T \setminus v := T \setminus \SUB(v)$ by usual graph difference to be the rooted subtree of $T$
    where all vertices and edges in $\SUB(v)$ (all vertices reachable from $v$, 
    including their associated edges) are deleted from $T$.
\end{statement3}

\newpage

\textbf{TEXT}

\begin{statement3}{(1.2)}{Remark}{(Number of vertices of some height in rooted r-ary Trees)}\strut\\[2pt]
    Let $h,r \in \mathbb{N}$ and $T$ be a rooted $r$-ary tree of height $h$.
    Then $T$ has exactly $r^{h'}$ vertices of height $h' \leq h$.
\end{statement3}

\begin{statement3}{(1.3)}{Corollary}{(Number of Leaves of $T \setminus v$)}\strut\\[2pt]
    Let $h,r \in \mathbb{N}$, $T$ be a rooted $r$-ary tree of height $h$, $T' \leq T$ and
    $v \in V(T') \setminus \{\ro(T')\}$ such that $\SUB_{T'}(v) \leq_r T$.
    If $L$ is the number of leaves of $T'$, then $T' \setminus v$ has $L - r^{h - \he_T(v)}$ leaves.

    \begin{proof}
        Since $\SUB_{T'}(v)$ is $r$-ary and has height $h - \he_T(v)$, we know $\SUB_{T'}(v)$ has
        $r^{h- \he_T(v)}$ leaves by (1.2).
        Thus $T' \setminus v = T' \setminus \SUB_{T'}(v)$ has $L - r^{h-\he_T(v)}$ leaves.
    \end{proof}
\end{statement3}

For us, intervals are over $\mathbb{N}_0$, so for $m,n \in \mathbb{N}_0$ we have $[m,n] := \{p \in \mathbb{N}_0 \mid
m \leq p \leq n\}$.\\
Now we will come to the relationship between $r$-ary codes and $r$-ary rooted trees.

\begin{statement3}{(1.4)}{Definition}{(r-ary Trees from r-ary Codes)}\strut\\[2pt]
    Let $q,r \in \mathbb{N}, A := [0,r-1]$ be the code-alphabet for some $r$-ary code $\mathcal{C}$ with word-lengths
    $l \in \mathbb{N}^q$. This choice of the code-alphabet can always be made since any other code-alphabet
    for $\mathcal{C}$ would stand in bijection to $A$.
    Set $h := \max\{l_i \mid i \in [1,q]\}$.
    Define $W := \bigcup_{i \in [0,h]} A^i$ to be the set of all words over $A$ of maximum length $h$. Thus
    $\mathcal{C} \subseteq W$. We construct a rooted $r$-ary tree $\T$ of height $h$ indexed by $W$ by setting
    $\ro(\T) := v_\varepsilon$, $V(\T) := \{v_w \mid w \in W\}$ and
    $E(\T) := \{(v_w,v_{w'}) \mid w,w' \in W, wx = w', x\in A\}$.
\end{statement3}
This gives us the correlation between tree-structure and prefix codes we talked about above:
$v_w \leq v_{w'} \,\Longleftrightarrow\, w \sqsubseteq w'$, and $\he(v_w) = |w|$ (Without
proof).
We give an example:

\begin{statement2}{(1.5)}{Examples.} Note that $\T$ is uniquely determined by $r$ and $h$.
    $\mathcal{T}_3^2$ is given by
    \begin{center}
        \begin{forest}
            [$\ro(\mathcal{T}_3^2)\text{=}v_\varepsilon$
                [$v_0$
                    [$v_{00}$],
                    [$v_{01}$],
                    [$v_{02}$]
                ],
                [$v_1$
                    [$v_{10}$],
                    [$v_{11}$],
                    [$v_{12}$]
                ],
                [$v_2$
                    [$v_{20}$],
                    [$v_{21}$],
                    [$v_{22}$]
                ]
            ],
        \end{forest}\\
    \end{center}
    We have $\he(v_\varepsilon) = 0$ and $\he(v_{12}) = 2$.
    $v_0 \leq v_{02}$ holds, $v_0 \leq v_{10}$ does \textbf{not}.\\
    The subtrees $\SUB(v_1)$ and $\mathcal{T}_3^2 \setminus v_1$ are given by:\\
    \begin{minipage}{.4\textwidth}
        \begin{center}
            \begin{forest}
                [$\ro(\SUB(v_1))\text{=}v_1$
                    [$v_{10}$],
                    [$v_{11}$],
                    [$v_{12}$]
                ]
            \end{forest}
        \end{center}
    \end{minipage}
    \begin{minipage}{.4\textwidth}
        \begin{center}
            \begin{forest}
                [$\ro(\mathcal{T}_3^2 \setminus v_1)\text{=}v_\varepsilon$
                    [$v_0$
                        [$v_{00}$],
                        [$v_{01}$],
                        [$v_{02}$]
                    ],
                    [$v_2$
                        [$v_{20}$],
                        [$v_{21}$],
                        [$v_{22}$]
                    ]
                ],
            \end{forest}\\
        \end{center}
    \end{minipage}\\[10pt]
    $\SUB(v_1)$ is a 3-ary rooted subtree of height $1$, but $\mathcal{T}_3^2 \setminus v_1$ is only
    a rooted subtree of height $3$, not $r$-ary for any $r \in \mathbb{N}$.
    We now have $\he_{\SUB(v_1)}(v_1) = 0, \he_{\SUB(v_1)}(v_{12}) = 1$, but still
    $\he_{\mathcal{T}_3^2 \setminus v_1}(v) = \he_{\mathcal{T}_3^2}(v)$ for $v \in V(\mathcal{T}_3^2 \setminus v_1)$.
\end{statement2}

\begin{statement3}{(1.6)}{Theorem}{(Kraft's Inequality)}\strut\\[2pt]
    Let $q,r \in \mathbb{N}, l \in \mathbb{N}^q$. Then there is an instantaneous $r$-ary code $\mathcal{C}$
    with word-lengths $l$ iff
    \begin{equation}
        \sum_{k=1}^{q} \frac{1}{r^{l_k}} \leq 1
    \end{equation}

    \begin{proof}
        If $q = 1$, then we always have an instantaneous code, and since $r \in \mathbb{N}$, (1) always holds
        as well.
        So assume w.l.o.g. that $q > 1$, $\forall i \in [1,q-1]: 0 < l_i \leq l_{i+1}$
        and that the code-alphabet of $\mathcal{C}$ is $[0,r-1]$.\\[10pt]
        We first show that (1) implies the existence of an $r$-ary prefix-code, which by
        \cite{ICT} is instantaneous.
        Set $h := l_q$ to be the maximum length of the supposed code-words of $\mathcal{C}$.
        Thus we should have, like in (1.4), that $\mathcal{C} \subseteq \bigcup_{i \in [0,h]} [0,r-1]^i =: W$, where
        $W$ is in bijection with $V(\T)$.
        So we construct the code-words $w_i$ of the prefix-code $\mathcal{C}$, with $|w_i| = l_i$ for $i \in [1,q]$
        via finite induction over $i$. The idea is to remove the subtrees rooted at $v_{w_i}$ and then
        chose $v_{w_{i+1}}$ from the remaining vertices to uphold the prefix property of $\mathcal{C}$,
        since for all $j \in [1,i]$ we have $l_j \leq l_{i+1}$ and for all $v_{w}$ with $w_j \sqsubseteq w$ we already removed $v_w$ before
        chosing $v_{w_{i+1}}$.\\[5pt]
        Let $i = 1$. Choose a code-word $w_1 \in [0,r-1]^{l_1}$ of length $l_1$. Since $w_1 \in W$ and $l_1 > 0$ we have
        $v_{w_1} \in V(\T) \setminus \{R(\T)\}$. Define $\mathcal{T}_0 := \T, \mathcal{T}_1 := \mathcal{T}_0 \setminus v_{w_1}$. We know
        from (1.3) that $\mathcal{T}_1$ has
        $$
            r^h - r^{h - \he(v_{w_1})} = r^h - r^{h - l_1} = r^h\left(1 - \sum_{k=1}^{1} \frac{1}{r^{l_k}}\right)
            > r^h\left(1 - \sum_{k=1}^{q} \frac{1}{r^{l_k}}\right) \up{\geq}{(1)} 0
        $$
        leaves. Now let $i \in [1,q-1]$ such that $\mathcal{C} := \{w_j \mid j \in [1,i]\}$ is a prefix-code
        with $|w_j| = l_j$\\[2pt]
        for $j \in [1,i]$ and such that $\mathcal{T}_i$ is a rooted subtree of $\T$ and has $r^h(1 - \sum_{k=1}^{i}\frac{1}{r^{l_k}}) > 0$ leaves.
        Then since $l_{i+1} \leq l_q = h$ we know that there must also be at least one vertex
        $v_w \in V(\mathcal{T}_i)$ with $\he(v_w) = l_{i+1}$ since trees are connected and we have a leaf.
        So set $w_{i+1} := w$. If we had $w_j \sqsubseteq w_{i+1}$ for
        some $j \in [1,i]$, then also $v_{w_j} \leq v_{w_{i+1}}$, but then
        $v_{w_{i+1}} \notin V(\mathcal{T}_{j-1} \setminus v_{w_j}) = V(\mathcal{T}_{j}) \subseteq V(\mathcal{T}_{i})$, a contradiction.
        Thus $\mathcal{C} := \{w_j \mid j \in [1, i+1]\}$ is still a prefix-code.
        If $i+1 = q$ we are done, as we have constructed the desired prefix-code. Otherwise,
        we set $\mathcal{T}_{i+1} := \mathcal{T}_i \setminus w_{i+1}$ and we get for the number of leaves:
        $$
            r^h\left(1-\sum_{k=1}^{i} \frac{1}{r^{l_k}}\right) - r^{h - l_{i+1}}
            = r^h\left(1-\sum_{k=1}^{i+1} \frac{1}{r^{l_k}}\right)
            > r^h\left(1-\sum_{k=1}^{q} \frac{1}{r^{l_k}}\right)
            \up{\geq}{(1)} 0
        $$
        Thus we constructed the desired prefix-code $\mathcal{C}$ by finite induction.\\[10pt]
        Now we show the existence of an instantaneous $r$-ary code $\mathcal{C}$ with word-lengths $l$ implies (1).
        We know from \cite{ICT} that $\mathcal{C}$ is a prefix-code. Let $i \in [1,q],
        w_i \in \mathcal{C}, |w_i| = l_i$ and set
        $$
            L_i := \{v_w \in V(\T) \mid w_i \sqsubseteq w \land |w| = h\}
            = \{v_w \in \SUB(v_{w_i}) \mid \he_\T(v_w) = h\}
        $$
        to be the set of leaves in $\SUB(v_{w_i})$. We know from (1.3) that $|L_i| = r^{h - l_i}$
        for $i \in [1,q]$.
        Furthermore we know that for each $i\neq j \in [1,q]$ $L_i \cap L_j = \varnothing$:\\
        Assume $i,j \in [1,q]$ and w.l.o.g. $i < j$. Let $v_w \in L_i \cap L_j$. Thus we get
        $$
            v_{w_i} \leq v_w \land v_{w_j} \leq v_w \,\Longrightarrow\, w_i \sqsubseteq w \land w_j \sqsubseteq w
            \up{\,\Longrightarrow\,}{$i < j$} w_i \sqsubseteq w_j
        $$
        which is a contradiction to the fact that $\mathcal{C}$ is a prefix-code.
        So now, since $\T$ only has $r^h$ leafs, we get what we wanted to show:
        $$
            r^h \geq |\bigcup_{i \in [1,q]} L_i| = \sum_{i = 1}^{q} |L_i| = \sum_{i=1}^{q} r^{h-l_i}
            = r^h\sum_{i=1}^{q} \frac{1}{r^{l_i}}
            \quad\,\Longleftrightarrow\,\quad \sum_{i=1}^{q} \frac{1}{r^{l_i}} \leq 1
        $$
    \end{proof}
\end{statement3}

One could assume, that because being instantaneous implies being uniquely decodable, the constraints
for being the latter are weaker. Suprisingly, this is not the case:

\begin{statement3}{(1.7)}{Theorem}{(McMillan's Inequality)}\strut\\[2pt]
    Let $q,r \in \mathbb{N}, l \in \mathbb{N}^q$. Then there is an uniquely decodable
    $r$-ary code $\mathcal{C}$ iff
    \begin{equation}
        \sum_{i=1}^{q} \frac{1}{r^{l_i}} \leq 1 \tag{1}
    \end{equation}

    \begin{proof}
        If we assume (1), then by Kraft's inequality we know that $\mathcal{C}$
        is instantaneous, which by \cite{ICT} implies unique decodability.\\[10pt]
        Now assume that $\mathcal{C}$ is a uniquely decodable $r$-ary code with word-lengths
        $l$.\\
        Let
        $
            K := \sum_{i=1}^{q} \frac{1}{r^{l_i}}
        $ and $n \in \mathbb{N}$.
        Then we have
        \begin{equation}
            K^n
            = \left(\sum_{i=1}^{q} \frac{1}{r^{l_i}}\right)^n
            = \sum_{i \in [1,q]^n}\prod_{k=1}^{n} \frac{1}{r^{l_{i_k}}}
            = \sum_{i \in [1,q]^n} r^{-\sum_{k=1}^{n} l_{i_k}} \tag{2}
        \end{equation}
        where the $i \in [1,q]^n$ represents $n$ choices of $q$ possible summands (with repitition).\\[10pt]
        Now there are many different $i \in [1,q]^n$ which have the same sum $\sum_{k=1}^{n} l_{i_k}$
        (consider permutations for example). Set $M := \max\{l_k\mid k \in [1,q]\}, m := \min\{l_k \mid k \in [1,q]\}$.
        Then we get $mn \leq \sum_{k=1}^{n} l_{i_k} \leq Mn$ for all $i \in [1,q]^n$ (3). We define for
        $j \in [mn,Mn], p \in [1,j]$:
        $$
            N_{j,p} := \{w_{i_1}w_{i_2}\cdots w_{i_p} \mid i \in [1,q]^n \land |w_{i_1}\cdots w_{i_n}| = j \}
        $$
        So $t \in N_{p,j}$ is a code-sequence of length $j$, consisting of $p$ code-words in $\mathcal{C}$.\\
        But since $\mathcal{C}$ is uniquely decodable, we know that
        $
            \forall t \in N_{j,p}: \exists!\ i \in [1,q]^n: t = w_{i_1}\cdots w_{i_n}
        $,
        meaning there is one and only one way to construct $t \in N_{p,k}$ from $p$ code-words of $\mathcal{C}$.\\
        This implies that
        \begin{equation}
            |\{i \in [1,q]^n \mid \sum_{k=1}^{n} l_{i_k} = j\}|
            = |\{i \in [1,q]^n \mid \sum_{k=1}^{n} |w_{i_k}| = j\}| \tag{4}
            = |N_{j,p}|
        \end{equation}
        Furthermore, since $N_{j,p} \subseteq [0,r-1]^j$, we have $|N_{j,p}| \leq r^j$. Thus, from (2), (3), (4) we get
        $$
            K^n = \sum_{j = mn}^{Mn} \frac{|N_{j,n}|}{r^j} \leq \sum_{j = mn}^{Mn} 1 = (l-m)n + 1
            \,\Longrightarrow\, \frac{K^n}{n} \leq (M-m) + \frac{1}{n}
        $$
        Now $M,m,K$ are fixed, while $n$ may be arbitrarily large. From Analysis we know
        that as $n \to \infty$, the only way that $\frac{K^n}{n}$ stays bounded is if $K \leq 1$.
        Thus we get the desired result:
        $$
            \sum_{i=1}^{q} \frac{1}{r^{l_i}} = K \leq 1
        $$
    \end{proof}
\end{statement3}

\begin{statement2}{(1.8)}{Corollary.}\strut\\[2pt]
    Let $r,q \in \mathbb{N}, l \in \mathbb{N}^q$. Then by the above inequalities we get
    that there exists an instantaneous $r$-ary code with word-lengths $l$ iff
    there exists an uniquely decodable $r$-ary code with word-lenghts $l$.
\end{statement2}

So now we have necessary conditions for when instantaneous $r$-ary Codes of some
given length exist for some $r \in \mathbb{N}$.
When searching / constructing a code, one usually wants a it to be instantaneous and have
its word lengths and code-alphabet as small as possible.
These properties are related through the Inequalites we proved.
In particular it is not possible to construct an instantaneous or uniquely decodable $r$-ary Code
with arbitrarily small word-lengths for some fixed $r$, neither for an arbitrarily small
$r$, given fixed word-lengths;\\
There exists a lower bound given by these Inequalities.

\begin{statement2}{(1.9)}{Remark.}
    Note that we know that if $q,r \in \mathbb{N}, l \in \mathbb{N}^q$
    satisfy Kraft's Inequality, there \textbf{exists} an instantaneous $r$-ary Code. This does in no way imply
    that every code with code-words of these lengths is instantaneous. Consider for example
    $r = 2, q = 3, l = (1,2,3)$. Then we have $\sum_{k=1}^{q} \frac{1}{r^{l_k}} = \frac{7}{8} \leq 1$,
    but the $2$-ary code $\{0, 01, 011\}$ is obviously not a prefix-code $\mathcal{C}$ and thus not instantaneous.
    Similarly, by (1.8) we know that if we have some uniquely decodable code, there \textbf{exists} an
    instantaneous code with the same word lengths, not that $\mathcal{C}$ is instantaneous. For this,
    consider the code $\{0,01,11\}$, which is uniquely decodable, but not instantaneous since $0 \sqsubseteq 01$.
\end{statement2}

As the proof for Kraft's Inequality is constructive, we conclude with an example of constructing an instantaneous code
for given constraints satisfying Kraft's Inequality:

\begin{statement2}{(1.10)}{Example.}
    Let $r = 2, q = 4, l = (1,2,3,4)$, which satisfy the Kraft Inequality. We may chose $w_1 \in [0,r-1]^{l_1} = [0,1]$
    so set $w_1 := 1$. Now consider $\mathcal{T}_2^{\max l} \setminus v_{w_1} = \mathcal{T}_2^4 \setminus v_1$:\\
    \begin{center}
        \begin{forest}
            [$\ro(\mathcal{T}_2^4 \setminus v_1)$
                [$v_0$
                    [$v_{00}$
                        [$v_{000}$
                            [$v_{0000}$],
                            [$v_{0001}$]
                        ],
                        [$v_{001}$
                            [$v_{0010}$],
                            [$v_{0011}$]
                        ]
                    ],
                    [$v_{01}$
                        [$v_{010}$
                            [$v_{0100}$],
                            [$v_{0101}$]
                        ],
                        [$v_{011}$
                            [$v_{0110}$],
                            [$v_{0111}$]
                        ]
                    ]
                ]
            ],
        \end{forest}\\
    \end{center}

\newpage

    \begin{minipage}{.5\textwidth}
        \begin{center}
        Now we chose one of the vertices at the\\
        height $l_2 = 2$, lets say $v_{00}$, and thus set\\
        $w_2 := 00$. Again consider
        $(\mathcal{T}_2^4 \setminus v_1) \setminus v_{00}$:\\[10pt]
        \begin{forest}
            [$\ro((\mathcal{T}_2^4 \setminus v_1) \setminus v_{00})$
                [$v_0$
                    [$v_{01}$
                        [$v_{010}$
                            [$v_{0100}$],
                            [$v_{0101}$]
                        ],
                        [$v_{011}$
                            [$v_{0110}$],
                            [$v_{0111}$]
                        ]
                    ]
                ]
            ]
        \end{forest}
        \end{center}
    \end{minipage}
    \begin{minipage}{.5\textwidth}
        \begin{center}
        For $l_3 = 3$ we chose $v_{011}$, $w:= 011$ and see\\
        $((\mathcal{T}_2^4 \setminus v_1) \setminus v_{00}) \setminus v_{011}$ is given by:\\[10pt]
        \begin{forest}
            [$\ro(((\mathcal{T}_2^4 \setminus v_1) \setminus v_{00}) \setminus v_{011})$
                [$v_0$
                    [$v_{01}$
                        [$v_{010}$
                            [$v_{0100}$],
                            [$v_{0101}$]
                        ]
                    ]
                ]
            ],
        \end{forest}
        \end{center}
    \end{minipage}\\[20pt]
        For $l_4 = 4$ we have 2 choices, the leaves of $((\mathcal{T}_2^4 \setminus v_1) \setminus v_{00}) \setminus v_{011}$, left and set $w_4 := 0100$.
        Now we have constructed the $r$-ary prefix-code $\mathcal{C} := \{1, 00, 011, 0100\}$ with
        word-lengths $l$, which we know is instantaneous.
\end{statement2}

\bibliography{lit}{}
\bibliographystyle{alpha}
\end{document}
